%! Author = Jason Cameron
%! Date = 2024-01-28

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serifhttps://www.overleaf.com/project/654b0f6eeb8408333a227c44
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Social Icons
\usepackage{fontawesome5}

\usepackage{supertabular}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.42\textwidth}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{%
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
        \textbf{#1} & #2 \\
        \ifx & #3 &%
        \else
        \textit{\small#3} &
        \fi
        \ifx & #4 &%
        \else
        \textit{\small #4} \\
        \fi
    \end{tabular*}\vspace{-7pt}%
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeTwoPositions}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & #2 \\
    \end{tabular*}
    \vspace{-7pt}
}
\newcommand{\resumeProjectHeadingWithDescription}[3]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & #2 \\
    \end{tabular*}
    \vspace{-7pt}
    \small{#3}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
\textbf{\Huge \scshape Jason Cameron} \\ \vspace{1pt}
\underline{\href{https://jasoncameron.dev}{\raisebox{-0.05\height}{\faDesktop} portfolio $|$}}
\underline{\href{mailto:jason@jasoncameron.dev}{\raisebox{-0.05\height}{\faEnvelope} jason@jasoncameron.dev}} $|$
\underline{\href{https://github.com/jasonlovesdoggo}{\raisebox{-0.05\height}{\faGithub} github.com/jasonlovesdoggo}} $|$
\underline{\href{https://www.linkedin.com/in/jsoncameron/}{\raisebox{-0.05\height}{\faLinkedin} linkedin.com/in/jsoncameron}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Project Metropolis}{Toronto, ON}
{Backend Lead}{Jun 2023 - Present}

\resumeItemListStart
\resumeItem{
Led team-wide effort to modernize API docs with django-spectacular, ensuring automated and up-to-date documentation
}
\resumeItem{
Streamlined deployment processes, resulting in a \emph{20\%} reduction in average build time. Simplified deployments to one-click scripts, improving overall system agility and minimizing average downtime by \emph{12\%}.
}
\resumeSubHeadingListEnd
\resumeSubSubheading
{Backend Member}{Sep. 2022 - Jun. 2023}
\resumeItemListStart
\resumeItem{
Implemented REST API filters, reducing page load times by \emph{25\%} and decreasing server load by \emph{3\%} during peak usage.}  % Todo: link to docs
\resumeItem{Engineered and implemented polymorphic comments, likes, view counts, and saves, enhancing platform features and laying the groundwork for future advancements.}
\resumeItemListEnd
\resumeSubHeadingListEnd
% \resumeItemListEnd
% \resumeSubheading
% {Co-Founder/Director of Technology and Outreach}{Nov. 2022 –- Sep. 2023}
% {Ontario Competitive Mathematics Committee}{Oakville, ON}
% \resumeItemListStart
% \resumeItem{Developed a script using \textbf{Google Maps API} to automate calculation of driving distances and lookup of school addresses on Google Sheets to streamlining outreach efforts by identifying schools within a certain radius}
% \resumeItem{Created a \textbf{custom Discord bot} to provide important information to new members, to automate the onboarding process}
% \resumeItem{Convinced 5 out of the contacted 16 schools' math clubs to join our flagship math contest, the OMC, accounting for \textbf{50.4\% of the 224 participants}}
% \resumeItem{Managed with a team of 3 developers to create a \textbf{mockup of our upcoming website using Figma} to ensure the website's functionality and create a seamless and engaging user experience}
% \resumeItemListEnd

% -----------Multiple Positions Heading-----------
% \resumeSubSubheading
%  {Software Engineer I}{Oct 2014 - Sep 2016}
%  \resumeItemListStart
%     \resumeItem{Apache Beam}
%       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%  \resumeItemListEnd
% \resumeSubHeadingListEnd
%-------------------------------------------

%-----------NOTABLE Projects-----------
\section{\texorpdfstring{\href{https://jasoncameron.dev/\#/projects}{Notable Projects}}{Notable Projects}}
\resumeSubHeadingListStart

\resumeProjectHeading
{\underline{\href{https://github.com/elebumm/RedditVideoMakerBot}{\textbf{RedditVideoMakerBot}}} $|$ \emph{Python, Reddit, FFmpeg, AWS Polly, Playwright, Web Scraping}} {May 2022 - Present}
\resumeItemListStart
\resumeItem{Simplified running the bot with a GUI for configuration which helped the bot grow to
\textbf{6000+} stars on GitHub with \textbf{100,000+} clones of the GitHub repository.}
\resumeItem{Enhanced bot's Text-to-Speech (TTS) functionality by reverse engineering the TikTok TTS API, and further        improved it by integrating several other TTS engines, such as the AWS Polly API.}
\resumeItem{Continuously improved and maintained the bot overcoming many challenges including but not limited to API
rate limiting, copywritten background videos, Reddit \& TikTok API changes \& challenges with the bot running
on \textbf{10,000+} different machines and across all major operating systems}
\resumeItemListEnd

\resumeProjectHeading
{\underline{\href{https://jasoncameron.dev/foodle}{\textbf{Foodle}}} $|$ \emph{TypeScript, Svelte, CSS, Python, Flask, Google Analytics}} {Aug. 2022 - Dec 2023}
\resumeItemListStart
\resumeItem{Individually created, maintained, documented, tested, deployed, and hosted my own twist of the popular
game Wordle with an additional set of twists and features.}
\resumeItem{Listened to feedback and grew the game to \textbf{650,000+} unique visitors with \textbf{5,000,000+} total page views.}
\resumeItemListEnd

\resumeProjectHeadingWithDescription
{\underline{\href{https://devpost.com/software/screentime-showdown}{\textbf{Screentime Showdown - Winner at HTV 8 }}} $|$ \emph{Express.js, React, Oauth2.0, Meta, PayBilt, Cohere}}{Oct. 2023}
{Helping people quit social media with the help of a friendly competition and some monetary gain. }
\resumeItemListStart
\resumeItem{Leveraged Meta's OAuth 2.0 \& Webhook API to enable real-time detection and response whenever a user opened Facebook or Instagram on any of their devices.}

\resumeItemListEnd


\resumeProjectHeadingWithDescription
{\underline{\href{https://devpost.com/software/physioquest}{\textbf{PhysioQuest - Winner at JamHacks 7 }}} $|$ \emph{Python, Django, HTML, JS, CSS, OpenCV, MongoDB}}{Jun. 2023}
{Gamifying physiotherapy with AI to encourage consistency and accuracy when completing exercises. }
\resumeItemListStart
\resumeItem{Designed and implemented the backend API and database models using \href{https://github.com/django/django}{Django} and \href{https://github.com/encode/django-rest-framework}{Django Rest Framework}}
\resumeItem{Integrated our trained \href{https://www.ibm.com/topics/computer-vision}{CV} model to the end user’s webcam using \emph{\href{https://channels.readthedocs.io/en/latest/}{Django channels}, \href{https://en.wikipedia.org/wiki/User_Datagram_Protocol}{UDP sockets} and \href{https://developer.mozilla.org/en-US/docs/Web/API/MediaStream}{HTML's MediaStream}}, enabling global device compatibility.}
\resumeItemListEnd

\resumeProjectHeadingWithDescription
{\underline{\href{https://github.com/wlmac/scavenger}{\textbf{Scavenger Hunt }}} $|$ \emph{Python, Django, CSS, JS, Oauth 2.0}}{Nov 2022-Present}{A scavenger hunt platform engineered to prevent cheating or RNG-based finds while ensuring fairness and integrity.}
\resumeItemListStart
\resumeItem{
Conceptualized and \href{https://github.com/wlmac/scavenger/commits?author=JasonLovesDoggo}{implemented} the backend's core functionality using \emph{Django}.
}
\resumeItem{Reorganized the architecture of the site by removing reliance on hard-coded configurations. Additionally, introduced functionality to support the execution of multiple concurrent hunts.}


\resumeItemListEnd


\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{William Lyon Mackenzie Collegiate Institute - Toronto, Ontario}{Sep. 2022- Jun. 2026}{}{}
\resumeItemListStart
\resumeItem{\textbf{Extracurriculars: }\href{https://maclyonsden.com}{School Website Team}  \emph{(Backend Lead / Vice-President)}, \href{https://mcpt.ca}{Competitive/Computer Programming Club}{(\emph{System Administrator Executive})}, Engineering Club (\emph{Tech Lead}), School Newspaper (\emph{Photographer / Quality Manager}), A/V Team (\emph{Crew Member / Club Liaison}), \href{https://flounder.news}{School Satirical Newspaper} (\emph{Web Developer}), Robotics Club (Member)}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\small{

\textbf{Languages}{: Python, Golang, JavaScript/TypeScript Java, Lua, HTML/CSS/SCSS} \\
\textbf{Server Tools}{: Linux, Caddy, Docker, Cloudflare, Amazon Web Services, Microsoft Azure, Google Cloud (GCP), Oracle Cloud (OCI)} \\
\textbf{Developer Tools}{: Git, VScode, InteliJ, MongoDB, PostgreSQL, SQLite, RocksDB, LevelDB, Redis, Django, FastAPI, Flask, React, Svelte, Gin, P5.js, Github Actions, Postman, Tailscale} \\
\textbf{Productivity and Design Tools}{: Miro, Notion, Microsoft Suite, Canva, Photoshop, Latex} \\
}

\end{document}
